RJObject Paper

### 2014-06-09 Documents/Paper/ms.tex
Factorise the prior
Paragraph on our motivation for using NS

>>>>

The prior for $N$, $\alpha$, and $\{x_i\}$ is usually factorised
in the following way:

\begin{eqnarray}
p(N, \alpha, \{x_i\}) &=& p(N) p(\alpha | N) p(\{x_i\} | \alpha, N) \\
&=& p(N) p(\alpha) \prod_{i=1}^N p(\{x_i\} | \alpha).
\end{eqnarray}

Here we have assumed the priors for $N$ and $\alpha$ are independent, and
the interim prior for $\{x_i\}$ is iid and does not depend on $N$.

In other studies, it has been common to do separate runs of Nested Sampling
with different values of $N$. Then, the posterior for $N$ can be calculated
based on the estimates of the evidence or marginal likelihood. Our motivation
for using Nested Sampling is different. With reversible jump MCMC it is possible
to obtain the posterior for $N$ with a single run. However, the exploration
of the posterior may be very difficult, and sometimes the problem may even
contain a phase transition. We use Nested Sampling to overcome these
difficulties.
